\racets: Policy{-}Agnostic Programming in Racket

### 2018-07-24 paper/paper.tex
abstract

\begin{abstract}lorem ipsum...\end{abstract}

>>>>

\begin{abstract}
Faceted Execution (FE) is a linguistic paradigm for dynamic
information flow control. Using faceted execution, secure program data
is represented by \emph{facets}: decision trees that encode how the
data should appear to its owner (represented by a label) versus everyone
else. When labels are allowed to be first-class (i.e., predicates that
decide at runtime which data to reveal), faceted execution enables
\emph{policy-agnostic programming}: a programming style that allows
privacy policies for data to be enforced independently of code that
computes on that data.

To date, implementations of faceted execution are relatively
heavyweight: requiring either changing the language runtime or the
application code (e.g., by using monads). In this paper, we present
\racets: an extension of Racket to faceted execution via macros. Given
Racket's highly-expressive macro system, our implementation follows
relatively directly from the semantics of faceted execution. To
demonstrate how \racets can be used for policy-agnostic programming,
we use it to build a web-based game of Battleship. Our implementation
sheds light on several interesting issues in interacting with code
written without faceted execution. \racets is currently available
under an open-source license on GitHub.

\end{abstract}
